Pre-processing high frequency animal tracking data

### 2020-10-07 01_background.Rmd
remove useless sections

This paper refers extensively to the `R` package `atlastools` (Gupte 2020), which can be installed from [Github.](https://github.com/pratikunterwegs/atlastools). 
See the repository for information on the build status.
The code chunk below shows how to install `atlastools`.

@@

```{r prep_libs_01_02}
# load smoove and datatable
library(smoove)
library(data.table)
```

```{r save_data}
data <- do_smoove_data()

# save simulated data
fwrite(data, "data/data_sim.csv")
```

Here, we write functions to add normally distributed errors to the position coordinates of the simulated data.

Example of introduced error.

```{r}
# load data
data <- fread("data/data_sim.csv")

# introduce errors to data
data[, `:=`(x_error = do_add_error(x, std_dev = 0.01),
            y_error = do_add_error(y, std_dev = 0.01))]

# plot real and introduced error
ggplot()+
  geom_path(data = data, aes(x, y),
            col = "blue")

atlastools::atl_compare_tracks(d2, data)
```

>>>>

This paper refers extensively to the `R` package `atlastools` (Gupte 2020), which can be installed from [Github.](https://github.com/pratikunterwegs/atlastools).

Releases of the package from Github can be found on Zenodo: [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4033155.svg)](https://doi.org/10.5281/zenodo.4033155)

The build status of the 'Master' branch is shown here.

<!-- badges: start -->
  [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/pratikunterwegs/atlastools?branch=master&svg=true)](https://ci.appveyor.com/project/pratikunterwegs/atlastools) 
  [![Build Status](https://travis-ci.org/pratikunterwegs/atlastools.svg?branch=master)](https://travis-ci.org/pratikunterwegs/atlastools) 
  [![codecov.io](https://codecov.io/github/pratikunterwegs/atlastools/coverage.svg?branch=master)](https://codecov.io/github/pratikunterwegs/atlastools/branch/master)
<!-- badges: end -->

The code chunk below shows how to install `atlastools`.

@@

First, we load `smoove` and `data.table`, as well as some helper functions that make use of them to simulate data for use.

```{r prep_libs_01_02, eval=FALSE}
# load smoove and datatable
library(smoove)
library(data.table)

# source helper functions
source("R/helper_functions.R")
```

```{r save_data}
data <- do_smoove_data()
# save simulated data
fwrite(data, "data/data_sim.csv")
```
